Evaluating Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe using radiocarbon data

### 2019-02-06 article/02_Materials_and_Methods.Rmd
citation for euclidian distance

From these time series another set of time series with a measure of cultural distance for each region-region relationship can be derived (Figure \ref{sed_region_matrix}). Cultural distance is defined here as the squared Euclidean distance (SED) between the trait proportions of two different regions at a certain point in time [@neimanStylisticVariationEvolutionary1995]. SED is a sensible metric here, because it is relatively simple, works with only a few assumptions and emphasises differences through squaring.

>>>>

From these time series another set of time series with a measure of cultural distance for each region-region relationship can be derived (Figure \ref{sed_region_matrix}). Cultural distance is defined here as the squared Euclidean distance (SED) between the trait proportions of two different regions at a certain point in time [@neimanStylisticVariationEvolutionary1995]. SED is a sensible metric here, because it is relatively simple, works with only a few assumptions and emphasises differences through squaring [@nakoinzFingerprintingIronAge2014].
